High resolution, annual maps of field boundaries for smallholder-dominated croplands at national scales

### 2022-02-06 inst/manuscript/manuscript.Rmd

## Cropland probabilities
```{r, echo=FALSE, message=FALSE, warning=FALSE}
initial <- train_val_sites$initial %>% as_tibble %>% group_by(Cluster) %>%
  count()
active <- train_val_sites$active %>% as_tibble %>% filter(usage == "train") %>% 
  group_by(aoi) %>% count()
typicaln <- raster::modal(initial$n) + raster::modal(active$n)
aoi10n <- (initial %>% filter(Cluster %in% 3) %>% pull(n)) + 
  (active %>% filter(aoi == "labeller10") %>% pull(n))
aoi14n <- (initial %>% filter(Cluster %in% 3) %>% pull(n)) + 
  (active %>% filter(aoi == "labeller14") %>% pull(n))
aoi15n <- (initial %>% filter(Cluster %in% 2) %>% pull(n)) + 
  (active %>% filter(aoi == "labeller15") %>% pull(n))
aoi3init <- initial %>% filter(!Cluster %in% 1:3) %>% pull(n)
aoi3n <- aoi3init + (active %>% filter(aoi == "labeller3") %>% pull(n))

@@

To make the initial maps of cropland probabilities, the active learning process ran for 3 iterations in 12 of 16 AOIs, varying from as little as 1 to as many as 4 iterations across the other 4 AOIs, with the number of iterations varying according to the performance of the starter models (i.e. AOIs with higher starting performance stopped after fewer iterations, see SI). Each AOI's model was trained by 300-500 randomly selected labels (Figure S7A), plus an additional `r aoi10n` - `r aoi15n` (typically `r typicaln`) labels within each AOI that were selected by active learning. Actively selected labels showed distinctive patterns in several AOIs (Figure S7B), such as concentrating along ecotones or the boundaries of agro-ecological zones. A total of `r ttrain` training and `r tval` validation labels were collected by 20 labellers to develop and assess model performance (Figure S8).

>>>>

## Cropland probabilities
```{r, echo=FALSE, message=FALSE, warning=FALSE}
initial <- train_val_sites$initial %>% as_tibble %>% group_by(Cluster) %>%
  count()
active <- train_val_sites$active %>% as_tibble %>% filter(usage == "train") %>% 
  group_by(aoi) %>% count()
typicaln <- raster::modal(initial$n) + raster::modal(active$n)
typicala <- raster::modal(active$n)
aoi10a <- active %>% filter(aoi == "labeller10") %>% pull(n)
aoi10n <- (initial %>% filter(Cluster %in% 3) %>% pull(n)) + 
  (active %>% filter(aoi == "labeller10") %>% pull(n))
aoi14n <- (initial %>% filter(Cluster %in% 3) %>% pull(n)) + 
  (active %>% filter(aoi == "labeller14") %>% pull(n))
aoi15n <- (initial %>% filter(Cluster %in% 2) %>% pull(n)) + 
  (active %>% filter(aoi == "labeller15") %>% pull(n))
aoi15a <- active %>% filter(aoi == "labeller15") %>% pull(n)
aoi3init <- initial %>% filter(!Cluster %in% 1:3) %>% pull(n)
aoi3n <- aoi3init + (active %>% filter(aoi == "labeller3") %>% pull(n))

@@

To make the initial maps of cropland probabilities, the active learning process ran for 3 iterations in 12 of 16 AOIs, varying from as little as 1 to as many as 4 iterations across the other 4 AOIs, with the number of iterations varying according to the performance of the starter models (i.e. AOIs with higher starting performance stopped after fewer iterations, see SI). Each AOI's model was trained by 300-500 randomly selected labels (Figure S7A), plus an additional `r aoi10a` - `r aoi15a` (typically `r typicala`) labels within each AOI that were selected by active learning. Actively selected labels showed distinctive patterns in several AOIs (Figure S7B), such as concentrating along ecotones or the boundaries of agro-ecological zones. A total of `r ttrain` training and `r tval` validation labels were collected by 20 labellers to develop and assess model performance (Figure S8).

### 2022-02-06 inst/manuscript/si.Rmd

---
title: "High resolution, annual maps of the characteristics of smallholder-dominated croplands at national scales"

subtitle: "Supporting Information"

@@

documentclass: article
classoption: a4paper
capsize: normalsize
fontsize: 11pt
geometry: margin=1in
linenumbers: yes
spacing: doublespacing
# abstract: The abstract can go either here or below
keywords: rmarkdown, reproducible science
bibliography: 
  - references.bib
csl: ecology.csl

@@

@@

- [`activemapper`](https://github.com/agroimpacts/activemapper): Contains the source code and derived data for this paper. The repository\footnote{github.com/agroimpacts/activemapper} will be opened following publication in a peer-reviewed journal.
- [`croplandmaps`](https://github.com/agroimpacts/croplandmaps_V2): Source code for web map displaying image composites and cropland probability maps. The repository\footnote{github.com/agroimpacts/croplandmaps\_V2} is open, and the field boundary datasets are available for download. 
- [`imager`](https:github.com/agroimpacts/imager): Source code for the image processing software. The repository\footnote{github.com/agroimpacts/imager} is currently private, but will be opened after completing a security audit. 
- [`labeller`](https:github.com/agroimpacts/labeller): Source code for the labelling platform. The repository\footnote{github.com/agroimpacts/labeller} is currently private, but will be opened after completing a security audit. 
- [`learner`](https:github.com/agroimpacts/learner): Source code for the active learning component. The repository\footnote{github.com/agroimpacts/learner} is open.
- [`segmenter`](https:github.com/agroimpacts/segmenter): Source code for the segmentation algorithm. The repository \footnote{github.com/agroimpacts/segmenter} is open.

\clearpage
# References
\singlespace

>>>>

---
title: "High resolution, annual maps of field boundaries for  smallholder-dominated croplands at national scales"
subtitle: "Supporting Information"

@@

documentclass: article
classoption: a4paper
capsize: normalsize
fontsize: 11pt
geometry: margin=1in
linenumbers: yes
spacing: doublespacing
keywords: rmarkdown, reproducible science
bibliography: 
  - references.bib
csl: ecology.csl

@@

- [`activemapper`](https://github.com/agroimpacts/activemapper): Repository\footnote{github.com/agroimpacts/activemapper} containing code and derived data used to write this paper. 
- [`imager`](https:github.com/agroimpacts/imager): Repository\footnote{github.com/agroimpacts/imager} containing code for the image processing software.
- [`labeller`](https:github.com/agroimpacts/labeller):  Repository\footnote{github.com/agroimpacts/labeller} containing code for the labelling platform. 
- [`learner`](https:github.com/agroimpacts/learner): Repository\footnote{github.com/agroimpacts/learner} containing code for the active learning component.
- [`segmenter`](https:github.com/agroimpacts/segmenter): Repository\footnote{github.com/agroimpacts/segmenter} containing code for the segmentation algorithm.
- [`mappingafrica.io`](https://mappingafrica.io): Project website\footnote{https://mappingafrica.io} linking to web map displaying field boundary maps. The web map is currently undergoing redevelopment, and will be hosted on a new URL and links download maps. In the interim, map data are available on request.

@@

# References
\singlespace

### 2022-02-06 inst/manuscript/si.tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  11pt,
  a4paper]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={High resolution, annual maps of the characteristics of smallholder-dominated croplands at national scales},
  pdfkeywords={rmarkdown, reproducible science},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Allowing for landscape pages
\usepackage{lscape}
\usepackage{graphicx}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}

@@

\title{High resolution, annual maps of the characteristics of
smallholder-dominated croplands at national scales}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Supporting Information}
\author{}
\date{\vspace{-2.5em}}

@@

@@

\begin{itemize}
\tightlist
\item
  \href{https://github.com/agroimpacts/activemapper}{\texttt{activemapper}}:
  Contains the source code and derived data for this paper. The
  repository\footnote{github.com/agroimpacts/activemapper} will be
  opened following publication in a peer-reviewed journal.
\item
  \href{https://github.com/agroimpacts/croplandmaps_V2}{\texttt{croplandmaps}}:
  Source code for web map displaying image composites and cropland
  probability maps. The
  repository\footnote{github.com/agroimpacts/croplandmaps\_V2} is open,
  and the field boundary datasets are available for download.
\item
  \href{https:github.com/agroimpacts/imager}{\texttt{imager}}: Source
  code for the image processing software. The
  repository\footnote{github.com/agroimpacts/imager} is currently
  private, but will be opened after completing a security audit.
\item
  \href{https:github.com/agroimpacts/labeller}{\texttt{labeller}}:
  Source code for the labelling platform. The
  repository\footnote{github.com/agroimpacts/labeller} is currently
  private, but will be opened after completing a security audit.
\item
  \href{https:github.com/agroimpacts/learner}{\texttt{learner}}: Source
  code for the active learning component. The
  repository\footnote{github.com/agroimpacts/learner} is open.
\item
  \href{https:github.com/agroimpacts/segmenter}{\texttt{segmenter}}:
  Source code for the segmentation algorithm. The repository
  \footnote{github.com/agroimpacts/segmenter} is open.
\end{itemize}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  11pt,
  a4paper]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={High resolution, annual maps of field boundaries for smallholder-dominated croplands at national scales},
  pdfkeywords={rmarkdown, reproducible science},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Allowing for landscape pages
\usepackage{lscape}
\usepackage{graphicx}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}

@@

\title{High resolution, annual maps of field boundaries for
smallholder-dominated croplands at national scales}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Supporting Information}
\author{}
\date{\vspace{-2.5em}}

@@

\begin{itemize}
\tightlist
\item
  \href{https://github.com/agroimpacts/activemapper}{\texttt{activemapper}}:
  Repository\footnote{github.com/agroimpacts/activemapper} containing
  code and derived data used to write this paper.
\item
  \href{https:github.com/agroimpacts/imager}{\texttt{imager}}:
  Repository\footnote{github.com/agroimpacts/imager} containing code for
  the image processing software.
\item
  \href{https:github.com/agroimpacts/labeller}{\texttt{labeller}}:
  Repository\footnote{github.com/agroimpacts/labeller} containing code
  for the labelling platform.
\item
  \href{https:github.com/agroimpacts/learner}{\texttt{learner}}:
  Repository\footnote{github.com/agroimpacts/learner} containing code
  for the active learning component.
\item
  \href{https:github.com/agroimpacts/segmenter}{\texttt{segmenter}}:
  Repository\footnote{github.com/agroimpacts/segmenter} containing code
  for the segmentation algorithm.
\item
  \href{https://mappingafrica.io}{\texttt{mappingafrica.io}}: Project
  website\footnote{https://mappingafrica.io} linking to web map
  displaying field boundary maps. The web map is currently undergoing
  redevelopment, and will be hosted on a new URL and links download
  maps. In the interim, map data are available on request.
\end{itemize}

@@
